\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Updated Figure 15 title

The MSE for different bin widths ($a_1$) using tSNE, UMAP, PHATE, PaCMAP, and TriMAP with default (hyper-)parameter setting (@fig-mnist-mse) were calculated. It is found that tSNE (@fig-mnist-mse (a)) provide the most reasonable representation for the digit 1 dataset, showing universally best. However, \gD{} representation shows a big non-linear cluster and a small cluster with a small gap (@fig-tsne-best).

@@

```{r}
#| fig-cap: "Different methods with default hyper-parameter settings"
#| label: fig-mnist-mse
#| fig-pos: H
#| out-height: 100%

>>>>

The MSE for different binwidths ($a_1$) using tSNE, UMAP, PHATE, PaCMAP, and TriMAP with default (hyper-)parameter setting (@fig-mnist-mse) were calculated. It is found that tSNE (@fig-mnist-mse (a)) provide the most reasonable representation for the digit 1 dataset, showing universally best. However, \gD{} representation shows a big non-linear cluster and a small cluster with a small gap (@fig-tsne-best).

@@

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the MNIST digit 1 data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout c is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-mnist-mse
#| fig-pos: H
#| out-height: 100%

### 2024-09-06 paper.tex
Updated Figure 15 title

The MSE for different bin widths (\(a_1\)) using tSNE, UMAP, PHATE,
PaCMAP, and TriMAP with default (hyper-)parameter setting
(Figure~\ref{fig-mnist-mse}) were calculated. It is found that tSNE
(Figure~\ref{fig-mnist-mse} (a)) provide the most reasonable
representation for the digit 1 dataset, showing universally best.
However, \gD{} representation shows a big non-linear cluster and a small
cluster with a small gap (Figure~\ref{fig-tsne-best}).

@@

\caption{\label{fig-mnist-mse}Different methods with default
hyper-parameter settings}

>>>>

The MSE for different binwidths (\(a_1\)) using tSNE, UMAP, PHATE,
PaCMAP, and TriMAP with default (hyper-)parameter setting
(Figure~\ref{fig-mnist-mse}) were calculated. It is found that tSNE
(Figure~\ref{fig-mnist-mse} (a)) provide the most reasonable
representation for the digit 1 dataset, showing universally best.
However, \gD{} representation shows a big non-linear cluster and a small
cluster with a small gap (Figure~\ref{fig-tsne-best}).

@@

\caption{\label{fig-mnist-mse}Assessing which of the 5 NLDR layouts on
the MNIST digit 1 data is the better representation using MSE for
varying binwidth (\(a_1\)). Colour used for the lines and points in the
left plot and in the scatterplots represents NLDR layout (a-e). Layout c
is universally poor. Layouts a that show two close clusters are
universally suboptimal. Layout a is the best choice.}
